---
title: "R Quiz 1"
output: 
  learnr::tutorial:
    progressive: TRUE
    allow_skip: FALSE
runtime: shiny_prerendered
date: "`r Sys.Date()`"
tutorial:
  id: "b215.f23.lab1.test"
  version: 0.5
---

```{r setup, include=FALSE}
library(learnr)
library(submitr)
library(gradethis)
library(tidyverse)
library(knitr)
library(ggmosaic)
library(praise)
library(utils)
tutorial_options(exercise.eval = TRUE, exercise.reveal_solution = FALSE, exercise.timelimit = 60)
gradethis::gradethis_setup(
  pass.praise = TRUE,
  fail.encourage = TRUE,
  fail.hint = TRUE
)

```
```{r, echo=F}
submitr::login_controls()
```

```{r context = "server", echo = FALSE}
options(tutorial.storage = "none")
vfun <- make_basic_validator(NULL, "hello") #basket::check_valid
storage_actions <- 
  record_gs4(
    key = "1slz3tMsSx0gNL6Zr5-fpXMkcpPAaziyRdufr5d6DofA",
    email = "bbitarello.teaching@gmail.com",
    vfun
  )
submitr::shiny_logic(input, output, session, vfun,
                     storage_actions)
```

```{css echo=FALSE}
 @media print {
  .topicsContainer,
  .topicActions,
  .exerciseActions .skip {
    display: none;
  }
  .topics .tutorialTitle,
  .topics .section.level2,
  .topics .section.level3:not(.hide) {
    display: block;
  }
  .topics {
    width: 100%;
  }
  .tutorial-exercise, .tutorial-question {
    page-break-inside: avoid;
  }
  .section.level3.done h3 {
    padding-left: 0;
    background-image: none;
  }
  .topics .showSkip .exerciseActions::before {
    content: "Topic not yet completed...";
    font-style: italic;
  }
}
/* paste CSS above here */
```

1. Below, assign the number 9 to the variable `a`.


```{r sim1, exercise=TRUE, allow_skip = FALSE}
               # assign 9 to a
```

```{r sim1-solution, allow_skip = FALSE}
a <- 9                
#Note: I am not sure how to allow multiple correct answers, say
# a<-9 and 
# a = 9
```


```{r sim1-check, allow_skip = FALSE}
grade_this_code()

```

2. Create a vector `b` with numbers, 2, 9, and 8, in that order.

```{r sim2, exercise = TRUE, allow_skip = FALSE}
b <- c()            # assign a vector with 2, 9 and 8, in that order, to b
```


```{r sim2-solution, allow_skip = FALSE}
b <- c(2,9,8)      # assign a vector with 2, 9 and 8, in that order, to b 
```

```{r sim2-check, allow_skip = FALSE}
grade_this_code()
```


3.Ask if `a` is equal to `b`.
```{r ex2setup}
a <- 9
b <- c(2,9,8)
```

```{r sim3, exercise = TRUE, exercise.setup = "ex2setup", allow_skip=FALSE}
                    # ask if a equals b 
```

```{r sim3-solution}
a == b               # ask if a equals b 
```

```{r sim3-check}
grade_this_code()
```

4.Multiply `a` and `b`.
```{r sim4, exercise = TRUE, exercise.setup = "ex2setup", allow_skip=FALSE}
                    # multiply a and b
```


```{r sim4-solution}
a * b             # multiply a and b 
```

```{r sim4-check}
grade_this_code()
```


5. R/Rstudio
```{r pRactice, echo=FALSE}
quiz(
    question("In the example above, what would R tell you when you ask it if a equals b?",
    answer("It doesn't return anything"),
    answer("`FALSE`"),
    answer("An error"),
    answer("The vector, `FALSE TRUE FALSE`", correct = TRUE),
    allow_retry = TRUE,
    correct = random_praise(),
    incorrect = random_encouragement(), random_answer_order = TRUE
  ),
  question("In the example above, what does multiplying a and b return?",
    answer("The vector, `2 9 8`"),
    answer("The vector, `18 81 72`", correct = TRUE),
    answer("The vector, `18 9 8`"),
    answer("The vector, `4 81 64`"),
    answer("An error"),
    allow_retry = TRUE,
    correct = random_praise(),
    incorrect = random_encouragement(), random_answer_order = TRUE
  ))
```


6. 
```{r quiz2, echo=FALSE}
quiz(caption = "Quiz - Install R",
  question("Is R free to download and use?",
    answer("Yes!", correct = TRUE, message = "R is free _and_ open source, which means that anyone can read, use, and copy the source code of the R language."),
    answer("No.")
  )
  ,
    question("What is the RStudio IDE?",
    answer("An application that makes it easier to use R.", correct = TRUE, message = "RStudio organizes your workspace and makes it easier to write, use, debug, and save R code. I highly recommend it and will rely on the RStudio IDE in several tutorials."),
    answer("An application that let's you use R without writing any code", message = "And thank goodness! Code provides a reproducible record of your work, which is essential for data science."),
    answer("A spreadsheet program like Microsoft Excel."),
    answer("Another name for R", message = "R and RStudio are two separate things. R is a language, like English. Think of RStudio as a program that helps you use the language, kind of like how a word processing program helps you write in English."),
    allow_retry = TRUE
  ),
  question("Is the RStudio IDE free to download and use?",
    answer("Yes!", correct = TRUE, message = "Like R, RStudio is free and open-source. There do exist professional versions of RStudio with enhanced features, but we will not rely on those features in these tutorials."),
    answer("No.", message = "Like R, RStudio is free and open-source. There do exist professional versions of RStudio with enhanced features, but we will not rely on those features in these tutorials.")
  ))
```



7. Perform the math calculations below:

a) The product of 15 by 17

```{r ex1, exercise=TRUE, allow_skip=FALSE}

```

```{r ex1-check}
grade_result(
  pass_if(~identical(.result, 255))
)

```

b) Thirteen to the power of 3:

```{r ex2, exercise=TRUE, allow_skip=FALSE}

```
```{r ex2-check}
grade_result(
  pass_if(~identical(.result, 2197))
)  
```  
c) Log of 14 (use the natural log):

```{r ex3, exercise=TRUE, allow_skip=FALSE}

```

```{r ex3-check}
grade_result(
  pass_if(~identical(.result,  log(14)))
)  
```  

d) Log of 100 (use base 10):

```{r ex4, exercise=TRUE, allow_skip=FALSE}

```

```{r ex4-check}
grade_result(
  pass_if(~identical(.result, 2))
)  
```  

e) The square root of 81:
```{r ex5, exercise=TRUE, allow_skip=FALSE}

```

```{r ex5-check}
grade_result(
  #pass_if(~any(((9-0.5)<.result)==TRUE)&any(((9+0.5)>.result)==TRUE)
      
    pass_if(~identical(.result, 9))
)  
```  

8. Prove your reached the end and you're not a robot my creating a variable called `my_name` with your last name spelled backwards followed by your first name. E.g., mine would be "olleratib_arabrab".
 


```{r sandbox1, exercise=TRUE, eval =TRUE}
# create variable my_name
# print variable my_name
```


**When you're done, in your browser go to file>Print and save your work as a PDF. Update this file into Moodle.**
The end!


